Title

### 2014-07-23 paper.tex
write text mining section

\begin{abstract}

% the freeform style of modern code review

@@

According to this process, reviewers' comment is the most important for the software quality. McIntosh et. al. \cite{Mcintosh} also found that components which were reviewed without discussion are likely to contain bugs. However, as tool supporting MCR allows reviewers freely write a message to the author, it is often seen that some comments are not clearly identify defects and ineffective. Microsoft developers reported that they only focus on minor logic errors rather than discussing deeper in design\cite{Bacchelli2013a}. Our observation in Qt project also correspond this finding. We found some comments is superficial as shown in Fig. \ref{fig:example}(a), some comments only discuss about Version Control System (e.g. Git) used in the project.

@@

\subsection{Text Mining Techniques}
\subsubsection{tf--idf}
\subsubsection{Similarity Measure}
\subsection{Evaluation Techniques}
\subsubsection{Precision and Recall}
\subsubsection{F-measure}

>>>>

\begin{abstract}
Software code review is an established method regarded as a best practice in Software Engineering to achieve a sufficient quality in software project. This method mainly intend to early identify defect before integrating changes. Nowadays, Modern Code Review (MCR)\cite{Bacchelli2013a}, less formal and lightweight code reviews have received much attention and  put into software development regularly in both industrial and OSS projects. A main benefit of MCR is the in-person meeting is not required as the formal inspection \cite{Fagan:1976:DCI:1661010.1661012}. Reviewers can discuss to find defects by comments through code review tool or mailing list. Then, developers will fix their changes following those comments. 
% the freeform style of modern code review

@@

According to this process, reviewers' comment is the most important for the software quality. McIntosh et. al. \cite{Mcintosh} also found that components which were reviewed without discussion are likely to contain bugs. However, as tool supporting MCR allows reviewers freely write a message to the author, it is often seen that some comments are not clearly identify defects and ineffective. Microsoft developers reported that they only focus on minor logic errors rather than discussing deeper in design\cite{Bacchelli2013a}. Our observation in Qt project also correspond this finding. We found some comments are superficial and unrelated to the proposed changes. For example, a superficial and unconfident reviewer as shown in Fig. \ref{fig:example}(a), a comment for rule of using Version Control System (e.g. Git) in the project Fig. \ref{fig:example}(b).

@@

\subsection{Text Mining Technique: Vector Space Model}
Vector Space Model (VSM) is well-known technique for information retrieval where documents written in unstructured natural language. In Software Engineering, VSM has been widely use to find relationship among documents in software issue tracking system\cite{Davies2012}.

\noindent\textbf{VSM} is a model for representing text documents as vectors. Thus, for a set of documents ($D$), each document ($d$) is represented as $\overrightarrow{V_d} = <w_{1,d},w_{2,d},w_{3,d},...w_{n,d}>$, where $n$ is the total number of unique terms occur in the set of documents; and $w_{t,d}$ is TF-IDF weighting of term $t$ calculated from term occurrence frequency. The weight of $w_{t,d}$   can be calculated following Equation \ref{eq:tf-idf} where $tf_{t,d}$ is frequency of term $t$ occurs in document $d$; and $|\{d' \in D | t \in d'\}|$ is the number of other documents $d'$ that also contain term $t$.

\begin{equation}
w_{t,d} = tf_{t,d} \times \log\frac{|D|}{1+|\{d' \in D | t \in d'\}|}
\label{eq:tf-idf}
\end{equation}
\pick{Equation need to be check.}

To calculate the similarity between two document vectors $\overrightarrow{V_c}$ and $\overrightarrow{V_d}$, we use Cosine similarity and Euclidian distance. 
\pick{Why we need two measurements?}

\noindent\textbf{Cosine similarity} measures similarity between two vectors using inner product as described in Equation \ref{eq:cosine}. The similarity value is ranging $[0,1]$ where 0 means there is no similarity and 1 means two vectors are textually similar.

\begin{equation}
\cos\theta(\overrightarrow{V_c},\overrightarrow{V_d}) = \frac{\sum_{i=1}^{|D|} w_{i,c} \times w_{i,d}}{\sqrt{\sum_{i=1}^{|D|} w^2_{i,c} \times \sum_{i=1}^{|D|} w^2_{i,d}}}
\label{eq:cosine}
\end{equation}

\noindent\textbf{Euclidian distance} measures ordinary distance between each element of two vectors using Equation \ref{eq:euclid}. The distance value is ranging $[0,\infty)$ where 0 means these vectors is same vector and a more distance means less similar vectors. This can be used to determine how dissimilarity between two vectors.

\begin{equation}
d(\overrightarrow{V_c},\overrightarrow{V_d}) = \sqrt{\sum_{i=1}^{|D|}(w_{i,c} - w_{i,d})^2}
\label{eq:euclid}
\end{equation}

\subsection{Estimating Similarity and Dissimilarity Criteria}
In our approach, we build our classification model by selecting similarity and dissimilarity that best discriminate comments. To do so, we use three traditional measurements: Precision, Recall, and F-measure.
\subsubsection{Precision and Recall}
\subsubsection{F-measure}
